\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Problem Set 1}
\author{Mason Ross Hayes}
\date{January 2020}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section{Introduction}
I have no experience with data science, but I have a strong interest in econometrics and a passion for economic issues such as industrial organization, macroeconomics, and game theory. Primarily, my interests have been influenced by the books that I have read from economists such as Philippon, Kahneman, Piketty, Tirole and others. From the influence of these readings, my main research interests are in industrial organization, economic inequality, and behavioral economics. I hope to do my final research project for this course on a topic within these fields.

Data science is an important part of economics that has, until now, been totally absent from my education. In this sense, I feel that I am under-prepared both for jobs and also for graduate studies. This is why I chose to take this class. My goal for this class is to learn R programming, data visualization, some basic machine learning, and data analysis that I will need for my studies, research, and later for my career.

From a more short term point of view, I am taking this course mainly to prepare myself for graduate school. I think that learning data science will be very valuable during my Master's studies, which I will start in Fall 2020 at the Toulouse School of Economics.



\section{Equation}



\begin{equation}
a^2 + b^2 = c^2
\end{equation}

\end{document}